Distributed Range-Only Localisation that Preserves Sensor and Navigator Privacies

### 2022-03-11 main.tex
Completed final proof read and updated diff in author's response

Typical cryptographic secrecy involves hiding all transferred data such that external parties in the communication network learn no new information from acquired encryptions. This can be achieved with common symmetric and public-key encryption schemes such as the Advanced Encryption Standard (AES) \cite{gueronIntelAdvancedEncryption2010} and the Rivest-Shamir-Adleman cryptosystem (RSA) \cite{rivestMethodObtainingDigital1978}, respectively. These scenarios, however, imply a trust between the encrypting and decrypting parties in the network. In some cases, this assumption cannot be made and control over what can be learnt or performed with encryptions is desired. This has led to several homomorphic and functional encryption schemes \cite{paillierPublicKeyCryptosystemsBased1999,shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013,chotardDecentralizedMultiClientFunctional2018} finding uses in various signal processing and localisation tasks. In \cite{alanwarPrOLocResilientLocalization2017}, homomorphic encryption is used to make time-independent model-free location estimates where an estimator cannot learn sensor measurements or locations. In \cite{aristovEncryptedMultisensorInformation2018}, similar secrecy is achieved with a linear Kalman filter when a hierarchical sensor network is present. In \cite{shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013}, privacy-preserving aggregation schemes are presented as a means to compute total powergrid usage without disclosing individual contributions, while in \cite{alexandruEncryptedCooperativeControl2019,alexandruPrivateWeightedSum2020}, private Weighted Sum Aggregation with centralised or hidden weights (pWSAc and pWSAh, respectively) are introduced as a means for computing local control inputs in a distributed environment without learning individual inputs.

Our contribution in this work presents a range-only localisation method meeting formal cryptographic requirements that ensure sensors keep their measurements, sensor variances and locations private while the navigator keeps its estimates private. We first define a novel notion for private linear combination aggregation and present an implementation that satisfies these requirements, before using it to derive a filter based on the Extended Kalman Filter with no hierarchical sensor layout assumptions. The linear combination aggregation scheme we put forward is in principle similar to the pWSAh scheme in \cite{alexandruPrivateWeightedSum2020}, however, a formal definition with different communication assumptions and leakages is given, crucial for its cryptographic security. To the best of the authors' knowledge, no existing method for Bayesian state estimation using range-only sensors and meeting the desired privacy requirements exists.

We motivate this scenario with the example of vehicle localisation in the presence of privately owned measurement stations. While the intention of measurement stations is the accurate navigation of passing vehicles, it may be reasonable to desire identifying details, such as hardware specifications or physical locations, to remain unknown to the other present stations and the navigator. Similarly, a navigator may not wish to disclose their most accurate location estimates to untrusted third-party measurers.

@@

Before giving a formal definition for the construction and security of our desired encryption scheme, we make the following assumptions on the capabilities of the participants.
\begin{LaTeXdescription}
    \item[Global Navigator Broadcast] We assume that broadcast information from the navigator is received by \textit{all} sensors involved in the protocol.
    \item[Consistent Navigator Broadcast] We assume that broadcast information from the navigator is received equally by all sensors. This means the navigator may not send different weights to individual sensors during a single instance $t$.
    \item[Honest-but-Curious Sensors] We adopt the honest-but-curious attacker model for all involved sensors, meaning that they follow the localisation procedure correctly but may store or use any gained sensitive information.
\end{LaTeXdescription}
We justify the global broadcast assumption by noting that any subset of sensors within the range of the navigator can be considered a complete group and treated as the global set for estimation purposes, generalising the method, while the wide-spread use of cheap non-directional antennas supports the assumption of consistent broadcasts. The final assumption refers to the known problem of misbehaving sensors \cite{lazosSeRLocSecureRangeindependent2004,ben-galOutlierDetection2005}, often requiring additional complicated detection mechanisms, and will not be considered in this work.

@@

As aggregation is typically performed on scalar inputs, we extend our notation to the context of multidimensional estimation data by letting an instance $t_{k,\tau}$ uniquely capture the scalar aggregation during an estimation timestep $k$ for a single element with position index $\tau$. To achieve this in practice, any injective function can be used, such as the concatenation $t_{k,\tau}=k\mathbin\|\tau$. The four algorithms defining our scheme are given as follows.
\begin{LaTeXdescription}
    \item[$\mathsf{Setup}(\kappa)$] On input parameter $\kappa$, generate two equal-length, sufficiently large, primes $p$ and $q$, and compute $N=pq$. Define a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$, choose the number of weights to combine, $m>1$, and set public parameter $\mathsf{pub}=H$, navigator public key $pk_0 = N$ and navigator private key $sk_0=(p,q)$. Sensor secret keys are generated by choosing $sk_i,\,i\in\{1,\dots,n-1\}$ uniformly from $\mathbb{Z}_{N^2}$ and setting the last key as $sk_n = -\sum^{n-1}_{i=1}sk_i$.

@@

In the form above, at every timestep $k$, all sensitive sensor information required for state estimation is captured in the measurement vector
\begin{equation}
    \vec{i}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\hat{\vec{x}}_{k|k-1}) + \mat{H}_{k,i}\hat{\vec{x}}_{k|k-1}) \label{eqn:measurement_vec}
\end{equation}
and the measurement matrix
\begin{equation}
    \mat{I}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:measurement_mat}
\end{equation}
namely, their measurements $z_{k,i}$, measurement variances $r_{k,i}$ and locations $\vec{s}_i$; captured in measurement functions $h_i$ and Jacobians $\mat{H}_{k,i}$. However, $\vec{i}_{k,i}$ and $\mat{I}_{k,i}$ also require the current predicted state estimate $\hat{\vec{x}}_{k|k-1}$ to be computed (in $h_i$ and $\mat{H}_{k,i}$). For this reason, our goal is to reformulate \eqref{eqn:measurement_vec} and \eqref{eqn:measurement_mat} to be computable at each sensor $i$ as a linear combination of functions of the navigator state estimate (the navigator weights), to be subsequently aggregated at the navigator. Application of the linear combination aggregation scheme proposed would in turn guarantee that sensors do not learn the navigator state, and the navigator learns only the aggregation required for updating its state estimate in \eqref{eqn:eif_info_vec_update} and \eqref{eqn:eif_info_mat_update}.

@@

The first thing we notice when wanting to decompose $\vec{i}_{k,i}$ and $\mat{I}_{k,i}$ to a linear combination of functions of $\hat{\vec{x}}_{k|k-1}$, is that $h_i$ cannot be rearranged in this way due to the present square-root. Similarly, the Jacobian of $h_i$ at $\hat{\vec{x}}_{k|k-1}$,
\begin{equation}
    \mat{H}_{k,i} = 
    \begin{bmatrix}
        \frac{\hat{x}_{k|k-1} - s_{x,i}}{\sqrt{(\hat{x}_{k|k-1} - s_{x,i})^2 + (\hat{y}_{k|k-1} - s_{y,i})^2}} \\
        \frac{\hat{y}_{k|k-1} - s_{y,i}}{\sqrt{(\hat{x}_{k|k-1} - s_{x,i})^2 + (\hat{y}_{k|k-1} - s_{y,i})^2}} \\
        0 \\
        \vdots
    \end{bmatrix}^\top\,,
\end{equation}
cannot be either. We, therefore, consider the modified measurement functions
\begin{equation}
    h'_i(\vec{x}) = h_i(\vec{x})^2\,. \label{eqn:modified_measurement_func}
\end{equation}
A measurement function in this form allows rearrangement of $h'_i$ and the corresponding Jacobian $\mat{H}'_{k,i}$ to a linear combination of powers of location elements in $\hat{\vec{x}}_{k|k-1}$, as
\begin{equation}
    \begin{split}
        h'_i(\vec{x}) &= \left\lVert
        \begin{bmatrix}
            x & y
        \end{bmatrix}^\top - \vec{s}_i\right\rVert^2 \\
        &= (x - s_{x,i})^2 + (y - s_{y,i})^2 \\
        &= x^2 + y^2 -2s_{x,i}x -2s_{y,i}y +s_{x,i}^2 +s_{y,i}^2
    \end{split}\,,
\end{equation}
and
\begin{equation}
    \mat{H}'_{k,i} = 
    \begin{bmatrix}
        2\hat{x}_{k|k-1} - 2s_{x,i} \\
        2\hat{y}_{k|k-1} - 2s_{y,i} \\
        0 \\
        \vdots
    \end{bmatrix}^\top\,. \label{eqn:modified_jacobian}
\end{equation}
Here, $h'_i$ and $\mat{H}'_{k,i}$ are linear combinations of $\hat{x}_{k|k-1}^2$, $\hat{y}_{k|k-1}^2$, $\hat{x}_{k|k-1}$ and $\hat{y}_{k|k-1}$. To show how the corresponding modified measurement vectors $\vec{i}'_{k,i}$ and matrices $\mat{I}'_{k,i}$ can be similarly rearranged and used for localisation, we also require the existence of measurements following a modified measurement model of the form
\begin{equation}
    z'_{k,i} = h'_i(\vec{x}_k)+v'_{k,i}\,, \label{eqn:modified_measurement_model}
\end{equation}
where $z'_{k,i}$ is the modified measurement, and noise term $v'_{k,i}$ is zero-mean and has a known variance $r'_{k,i}$.

@@

\section{Conclusion} \label{sec:conclusion}
We have presented a localisation filter in the presence of range-only sensors, which preserves both navigator and sensor privacies. A suitable cryptographic scheme has been introduced and a filter implementation compared and evaluated. Privacy-preserving range-only localisation is suitable for use in environments where sensor networks are untrusted or location is considered private and we hope to extend the method to broader measurement models in the future. Additional future work includes exploring more computationally efficient encryption schemes and filter reformulations to decrease the filter update duration, exploring the possible security implications of sensors that are not only honest-but-curious and expanding the LCAO notion to guarantee that consistent broadcasts are always made by the navigator.

@@

%\vspace{-1\baselineskip}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/marko_ristic}}]{Marko Ristic}
received his software engineering diploma in 2018 at the University of Melbourne, Australia. In 2019, he began work as a researcher at the Intelligent Sensor-Actuator-Systems Laboratory, Karlsruhe Institute of Technology (KIT), Germany, and since 2021, he has been pursuing a Ph.D. at the Autonomous Multisensor Systems (AMS) group, Otto von Guericke University, Germany. His research interests include encrypted and privacy-preserving signal processing, focusing on state estimation, sensor fusion, and distributed localisation.
\end{IEEEbiography}

%\vspace{-1\baselineskip}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/benjamin_noack}}]{Benjamin Noack}
is a professor of Computer Science at the Otto von Guericke University Magdeburg in Germany and head of the Autonomous Multisensor Systems (AMS) group. He received his diploma in computer science from the Karlsruhe Institute of Technology (KIT), Germany, in 2009. Afterward, he obtained his Ph.D. in 2013 at the Intelligent Sensor-Actuator-Systems Laboratory, Karlsruhe Institute of Technology (KIT), Germany. His research interests are in the areas of multi-sensor data fusion, distributed and decentralized Kalman filtering, combined stochastic and set-membership approaches to state estimation, and event-based systems.
\end{IEEEbiography}

%\vspace{-1\baselineskip}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/uwe_d_hanebeck}}]{Uwe D. Hanebeck}
is a chaired professor of Computer Science at the Karlsruhe Institute of Technology (KIT) in Germany and director of the Intelligent Sensor-Actuator-Systems Laboratory (ISAS). He obtained his Ph.D. degree in 1997 and his habilitation degree in 2003, both in Electrical Engineering from the Technical University in Munich, Germany. His research interests are in the areas of information fusion, nonlinear state estimation, stochastic modeling, system identification, and control with a strong emphasis on theory-driven approaches based on stochastic system theory and uncertainty models. He is author and coauthor of more than 500 publications in various high-ranking journals and conferences and an IEEE Fellow.
\end{IEEEbiography}

>>>>

Typical cryptographic secrecy involves hiding all transferred data such that external parties in the communication network learn no new information from acquired encryptions. This can be achieved with common symmetric and public-key encryption schemes such as the Advanced Encryption Standard (AES) \cite{gueronIntelAdvancedEncryption2010} and the Rivest-Shamir-Adleman cryptosystem (RSA) \cite{rivestMethodObtainingDigital1978}, respectively. These scenarios, however, imply trust between the encrypting and decrypting parties in the network. In some cases, this assumption cannot be made and control over what can be learnt or performed with encryptions is desired. This has led to several homomorphic and functional encryption schemes \cite{paillierPublicKeyCryptosystemsBased1999,shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013,chotardDecentralizedMultiClientFunctional2018} finding uses in various signal processing and localisation tasks. In \cite{alanwarPrOLocResilientLocalization2017}, homomorphic encryption is used to make time-independent model-free location estimates where an estimator cannot learn sensor measurements or locations. In \cite{aristovEncryptedMultisensorInformation2018}, similar secrecy is achieved with a linear Kalman filter when a hierarchical sensor network is present. In \cite{shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013}, privacy-preserving aggregation schemes are presented as a means to compute total power grid usage without disclosing individual contributions, while in \cite{alexandruEncryptedCooperativeControl2019,alexandruPrivateWeightedSum2020}, private Weighted Sum Aggregation with centralised or hidden weights (pWSAc and pWSAh, respectively) are introduced as a means for computing control inputs in a distributed network without learning individual contributions.

Our contribution in this work presents a range-only localisation method meeting formal cryptographic requirements that ensure sensors keep their measurements, sensor variances and locations private while the navigator keeps its estimates private. We first define a novel cryptographic notion for linear combination aggregation and present an implementation satisfying the requirements, before using it to derive a filter based on the Extended Kalman Filter with no hierarchical sensor layout assumptions. The linear combination aggregation scheme is in principle similar to the pWSAh scheme in \cite{alexandruPrivateWeightedSum2020}, however, a formal definition with different communication assumptions and leakages is given, crucial for its cryptographic security. To the best of the authors' knowledge, no existing method for Bayesian state estimation using range-only sensors and meeting the desired privacy requirements exists.

We motivate this scenario with an example of vehicle localisation in the presence of privately owned measurement stations. While the intention of stations is the accurate navigation of passing vehicles, it may be reasonable to desire identifying details, such as hardware specifications or physical locations, to remain unknown to the other stations and the navigator. Similarly, a navigator may not wish to disclose their accurate location estimates to untrusted third-party measurers.

@@

Before giving a formal definition for the construction and security of our desired encryption scheme, we make the following assumptions on the capabilities of the participants.
\begin{LaTeXdescription}
    \item[Global Navigator Broadcast] We assume that broadcast information from the navigator is received by \textit{all} sensors involved in the protocol.
    \item[Consistent Navigator Broadcast] We assume that broadcast information from the navigator is received equally by all sensors. This means the navigator may not send different weights to individual sensors during a single instance $t$.
    \item[Honest-but-Curious Sensors] We adopt the honest-but-curious attacker model for all involved sensors, meaning that they follow the localisation procedure correctly but may store or use any gained sensitive information.
\end{LaTeXdescription}
We justify the global broadcast assumption by noting that any subset of sensors within the range of the navigator can be considered a group and treated as the global set during estimation, generalising the method, while the wide-spread use of cheap non-directional antennas supports the assumption of consistent broadcasts. The final assumption refers to the known problem of misbehaving sensors \cite{lazosSeRLocSecureRangeindependent2004,ben-galOutlierDetection2005}, often requiring additional complicated detection mechanisms, and will not be considered in this work.

@@

As aggregation is typically performed on scalar inputs, we extend our notation to the context of multidimensional estimation data by letting an instance $t_{k,\tau}$ uniquely capture the scalar aggregation during an estimation timestep $k$ for a single element with position index $\tau$. To achieve this in practice, any injective function can be used, such as the concatenation $t_{k,\tau}=k\mathbin\|\tau$. The four algorithms defining our scheme are given as follows.
\begin{LaTeXdescription}
    \item[$\mathsf{Setup}(\kappa)$] On input parameter $\kappa$, generate two equal-length, sufficiently large, primes $p$ and $q$, and compute $N=pq$. Define a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$, choose the number of weights to combine, $m>1$, and set public parameter $\mathsf{pub}=H$, navigator public key $pk_0 = N$ and navigator private key $sk_0=(p,q)$. Sensor secret keys are generated by choosing $sk_i,\,i\in\{1,\dots,n-1\}$ uniformly from $\mathbb{Z}_{N^2}$ and setting the last key to $sk_n = -\sum^{n-1}_{i=1}sk_i$.

@@

In the form above, at every timestep $k$, all sensitive sensor information required for state estimation is captured in the measurement vector
\begin{equation}
    \vec{i}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\hat{\vec{x}}_{k|k-1}) + \mat{H}_{k,i}\hat{\vec{x}}_{k|k-1}) \label{eqn:measurement_vec}
\end{equation}
and the measurement matrix
\begin{equation}
    \mat{I}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:measurement_mat}
\end{equation}
namely, their measurements $z_{k,i}$, measurement variances $r_{k,i}$ and locations $\vec{s}_i$; captured in measurement functions $h_i$ and Jacobians $\mat{H}_{k,i}$. To compute $\vec{i}_{k,i}$ and $\mat{I}_{k,i}$, however, the current predicted state estimate $\hat{\vec{x}}_{k|k-1}$ is also required (in $h_i$ and $\mat{H}_{k,i}$). Therefore, our goal is to rearrange \eqref{eqn:measurement_vec} and \eqref{eqn:measurement_mat} as a linear combination of functions of $\hat{\vec{x}}_{k|k-1}$ (the navigator weights) computable at each sensor $i$, to be subsequently aggregated at the navigator. Application of the linear combination aggregation scheme proposed in turn guarantees that sensors do not learn the navigator state, and the navigator learns only the aggregation required for updating its state estimate in \eqref{eqn:eif_info_vec_update} and \eqref{eqn:eif_info_mat_update}.

@@

The first thing we notice when wanting to rearrange $\vec{i}_{k,i}$ and $\mat{I}_{k,i}$ to a linear combination of functions of $\hat{\vec{x}}_{k|k-1}$, is that $h_i$ cannot be rearranged in this way due to the present square-root. Similarly, the Jacobian of $h_i$ at $\hat{\vec{x}}_{k|k-1}$,
\begin{equation}
    \mat{H}_{k,i} = 
    \begin{bmatrix}
        \frac{\hat{x}_{k|k-1} - s_{x,i}}{\sqrt{(\hat{x}_{k|k-1} - s_{x,i})^2 + (\hat{y}_{k|k-1} - s_{y,i})^2}} \\
        \frac{\hat{y}_{k|k-1} - s_{y,i}}{\sqrt{(\hat{x}_{k|k-1} - s_{x,i})^2 + (\hat{y}_{k|k-1} - s_{y,i})^2}} \\
        0 \\
        \vdots
    \end{bmatrix}^\top\,,
\end{equation}
cannot be either. We, therefore, consider the modified measurement functions
\begin{equation}
    h'_i(\vec{x}) = h_i(\vec{x})^2\,. \label{eqn:modified_measurement_func}
\end{equation}
A measurement function in this form allows rearrangement of $h'_i$ and the corresponding Jacobian $\mat{H}'_{k,i}$ to a linear combination of powers of location elements in $\hat{\vec{x}}_{k|k-1}$, as
\begin{equation}
    \begin{split}
        h'_i(\vec{x}) &= \left\lVert
        \begin{bmatrix}
            x & y
        \end{bmatrix}^\top - \vec{s}_i\right\rVert^2 \\
        &= (x - s_{x,i})^2 + (y - s_{y,i})^2 \\
        &= x^2 + y^2 -2s_{x,i}x -2s_{y,i}y +s_{x,i}^2 +s_{y,i}^2
    \end{split}\,,
\end{equation}
and
\begin{equation}
    \mat{H}'_{k,i} = 
    \begin{bmatrix}
        2\hat{x}_{k|k-1} - 2s_{x,i} \\
        2\hat{y}_{k|k-1} - 2s_{y,i} \\
        0 \\
        \vdots
    \end{bmatrix}^\top\,. \label{eqn:modified_jacobian}
\end{equation}
Here, $h'_i$ and $\mat{H}'_{k,i}$ are linear combinations of $\hat{x}_{k|k-1}^2$, $\hat{y}_{k|k-1}^2$, $\hat{x}_{k|k-1}$ and $\hat{y}_{k|k-1}$. To show how the corresponding modified measurement vectors $\vec{i}'_{k,i}$ and matrices $\mat{I}'_{k,i}$ can be similarly rearranged and used for localisation, we also require the existence of measurements following a modified measurement model of the form
\begin{equation}
    z'_{k,i} = h'_i(\vec{x}_k)+v'_{k,i}\,, \label{eqn:modified_measurement_model}
\end{equation}
where $z'_{k,i}$ is the modified measurement, and noise term $v'_{k,i}$ is zero-mean and has a known variance $r'_{k,i}$.

@@

\section{Conclusion} \label{sec:conclusion}
We have presented a localisation filter in the presence of range-only sensors, which preserves both navigator and sensor privacies. A suitable cryptographic scheme has been introduced and a filter implementation compared and evaluated. Privacy-preserving range-only localisation is suitable for use in environments where sensor networks are untrusted or location is considered private and we hope to extend the method to broader measurement models in the future. Additional future work includes exploring more computationally efficient encryption schemes, the security implications of sensors that are not only honest-but-curious and expanding the LCAO notion to enforce the consistent broadcast assumption.

@@

\vspace{-2\baselineskip}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/marko_ristic}}]{Marko Ristic}
received his software engineering diploma in 2018 at the University of Melbourne, Australia. In 2019, he began work as a researcher at the Intelligent Sensor-Actuator-Systems Laboratory, Karlsruhe Institute of Technology (KIT), Germany, and since 2021, he has been pursuing a Ph.D. at the Autonomous Multisensor Systems (AMS) group, Otto von Guericke University, Germany. His research interests include encrypted and privacy-preserving signal processing, focusing on state estimation, sensor fusion, and distributed localisation.
\end{IEEEbiography}

\vspace{-2\baselineskip}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/benjamin_noack}}]{Benjamin Noack}
is a professor of Computer Science at the Otto von Guericke University Magdeburg in Germany and head of the Autonomous Multisensor Systems (AMS) group. He received his diploma in computer science from the Karlsruhe Institute of Technology (KIT), Germany, in 2009. Afterward, he obtained his Ph.D. in 2013 at the Intelligent Sensor-Actuator-Systems Laboratory, Karlsruhe Institute of Technology (KIT), Germany. His research interests are in the areas of multi-sensor data fusion, distributed and decentralized Kalman filtering, combined stochastic and set-membership approaches to state estimation, and event-based systems.
\end{IEEEbiography}

\vspace{-2\baselineskip}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/uwe_d_hanebeck}}]{Uwe D. Hanebeck}
is a chaired professor of Computer Science at the Karlsruhe Institute of Technology (KIT) in Germany and director of the Intelligent Sensor-Actuator-Systems Laboratory (ISAS). He obtained his Ph.D. degree in 1997 and his habilitation degree in 2003, both in Electrical Engineering from the Technical University in Munich, Germany. His research interests are in the areas of information fusion, nonlinear state estimation, stochastic modeling, system identification, and control with a strong emphasis on theory-driven approaches based on stochastic system theory and uncertainty models. He is author and coauthor of more than 500 publications in various high-ranking journals and conferences and an IEEE Fellow.
\end{IEEEbiography}
